Analyzing Toronto's Dining Scene: Public Food Safety and Economic Indicators in Focus

### 2024-01-24 Outputs Folder/paper_final.qmd
Fixed typos and updated appendix

\section{Clean Dinesafe Dataset} 
\label{app:clean-dinesafe-dataset} 
Considering the huge content of the data set, this appendix contains a preview of the cleaned data set that has been used for the research. Original data is avaliable at https://github.com/ShadyEvan4830/Tonronto_Dinesafe_DataAnalysis.git
```{r}
#| echo: false
#| message: false
#| warning: false
library(dplyr)
library(magrittr)  
library(kableExtra)
library(readr)
library(tidyr)
library(knitr)

file_path <- "/cloud/project/Inputs Folder/Data/Clean_Dinesafe_Data.csv"
dataset <- read_csv(file_path)

processed_dataset <- dplyr::select(dataset, 
                                   Inspection_Dates = `Inspection Date`, 
                                   Establishment_Type = `Establishment Type`,
                                   Establishment_Status = `Establishment Status`,
                                   Severity,
                                   Action,
                                   Min_Inspections_Per_Year = `Min. Inspections Per Year`)

summary_table <- dplyr::group_by(processed_dataset, Establishment_Type, Establishment_Status) %>%
  dplyr::summarise(Total_Count = n(), 
                   Avg_Min_Inspections = mean(Min_Inspections_Per_Year, na.rm = TRUE)) %>%
  dplyr::arrange(Establishment_Type, Establishment_Status)

#knitr::kable(summary_table)

kable(head(summary_table,20), format = "latex", longtable = TRUE, booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "repeat_header"))

>>>>

\section{Clean Dinesafe Dataset} 
\label{app:clean-dinesafe-dataset} 
Considering the huge content of the data set, this appendix contains a preview of the cleaned data set that has been used for the research. Original data is avaliable at https://github.com/ShadyEvan4830/Tonronto_Dinesafe_DataAnalysis.git
```{r}
#| echo: false
#| message: false
#| warning: false
# Load necessary libraries
library(readr)
library(dplyr)
library(knitr)
library(kableExtra)

file_path <- "/cloud/project/Inputs Folder/Data/Clean_Dinesafe_Data.csv"

dataset <- read_csv(file_path)

selected_dataset <- dataset %>%
  select(Establishment_Type = `Establishment Type`,
         Establishment_Status = `Establishment Status`,
         Min_Inspections_Per_Year = `Min. Inspections Per Year`,
         Severity) %>%
  head(20)

kable(selected_dataset, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "repeat_header"))
